\section{Aims \& Objectives}
\begin{clause}
	The aims of the society are:
\end{clause}

	\begin{subclause}
		 To provide opportunities for the Students' Union ``hackers''\footnote{A person who delights in exploring the details of programmable systems and stretching their capabilities; solving problems in a playful and 		creative way.} and technologists from all backgrounds and interests within technology to interact with one another.
	\end{subclause}
	
	\begin{subclause}
 		To aid in expanding the skills of the Students' Union members through collaboration and pursuit of common interests, related to the field of ``hacking'', including programming, electronics, development and technology start-ups.
	\end{subclause}
	
	\begin{subclause}
		To provide an environment in which Student's Union members can express their ideas and build great things together.
	\end{subclause}

\begin{clause}
	The objectives of the society are:
\end{clause}
	
	\begin{subclause}
 		To hold events in which members can meet to share and develop ideas.
	\end{subclause}
	
	\begin{subclause}
 		To hold events in which experienced members can share their experience of a particular area with other members, i.e. tutorials on a particular programming language.
	\end{subclause}
	
	\begin{subclause}
 		To hold events that allow members to expand their knowledge and understanding of technologies through workshops, external speaker engagements, and meetups.
	\end{subclause}
	
	\begin{subclause}
 		To organise trips and events that allow members to engage with the wider technology community.
	\end{subclause}
	
	\begin{subclause}
		To represent the interests of the members at relevant external events, such as hackathons, meetups, and conferences.
	\end{subclause}
	
	\begin{subclause}
 		To attract students from a diverse range of courses, to enalbe those that may not have scope to express their interests on their course to do so.
	\end{subclause}
	
	\begin{subclause}
 		To maintain a strong relationship with the wider UK and European student hacker community.
	\end{subclause}
